---
title: "R Notebook"
output: html_notebook
---



```{r}
studio <- read.csv("C:/Users/Owner/OneDrive/Documente/data/Studio assessment 2017-2022.csv")
```

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(readr)
library(tidyr)
```



Count for each column
```{r}

#Q1 <- studio %>% count(NYC.Metro.Area.)
#pie(table(studio$NYC.Metro.Area.))

slices <- c(11, 20)
lbls <- c("No-", "Yes-")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="")
pie(slices,labels = lbls, col=wes_palette(n=2, "GrandBudapest1"),
   main="Number of NYC Metro Area Clients \n in GSAPP Studios (2017-2022)")
#pie(slices, labels = lbls,explode=0.1, main="Number of Clients Located in NYC Metro Area")

```
Question 2
```{r}

slices <- c(16, 13, 2)
lbls <- c("No-", "Yes-", "Unknown-")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="")
pie(slices,labels = lbls, col=c("#143151", "#5A435F","#C3C7E0"),
   main="Number of NYC Neighborhood-Specific Clients \n in GSAPP Studios (2017-2022)")

#use the Wednesday color palette c("#143151", "#5A435F","#C3C7E0", "#0A0C18")
#wesanderson: col=wes_palette(n=3, name="GrandBudapest1")
#col=rainbow(length(lbls)),
```
Practice making it more beautiful with ggplot and wes anderson palette
```{r}

library(wesanderson)
paint <- wes_palette("GrandBudapest2", n=8, type="continuous")

concerns <- words100 %>% slice_max(freq, n=8) #table with 30 rows and columns
concerns %>% ggplot(aes(x=word, y=freq)) + geom_col() + geom_bar(stat='identity', fill=paint) + ggtitle("The Top 8 Community Concerns Recorded 1 Year After Hurricane Maria")
```



Q3
```{r}
slices <- c(17, 10, 1, 3)
lbls <- c("No-", "Yes-", "Unknown-", "No and Yes-")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="")
pie(slices,labels = lbls, col=wes_palette(n=4, "GrandBudapest1"),
   main="Total Percentage of BIPOC Clients in \n GSAPP Studios (2017-2022)")
```

Q4
```{r}
slices <- c(25, 4, 2)
lbls <- c("No-", "Yes-", "Unknown-")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="")
pie(slices,labels = lbls, col=wes_palette(n=3, "GrandBudapest1"),
   main="Percentage of BIPOC Clients from \n Community Based Organizations in GSAPP Studios (2017-2022)")
```
Q6
```{r}
slices <- c(21, 5, 5)
lbls <- c("No-", "Yes-", "Unknown (Spring 2022)-")
pct <- round(slices/sum(slices)*100)
lbls <- paste(lbls, pct) # add percents to labels
lbls <- paste(lbls,"%",sep="")
pie(slices,labels = lbls, col=c("#143151", "#5A435F","#C3C7E0"),
   main="Ongoing, Continued Engagement with Clients \n from GSAPP Studios (2017-2022)")
```

Make a heat map with the boroughs:

I need to make a separate dataframe where the Columns indicating it is NYC-based is Yes
```{r}



nyc <- studio %>% filter(grepl('YES', NYC.Metro.Area.))

# %>%
#    filter(month==1) %>%
#    filter(day==1)

```



January 5th 2023: Pick up here, to do a count of all of the borough by combining the dataframes then project it into the map of NYC. Figure out what to do with Newark and Hudson Valley.


Mutate the column to add the Borough
```{r}

library(tidyverse)
library(magrittr)

MN <- nyc %>% filter(Borough=="Manhattan")
MN1 <- MN %>% mutate(Borough=str_replace(Borough, "Manhattan", "1"))
MN2 <- nyc %>% filter(Borough1=="Manhattan")
MN2 <- MN2 %>% mutate(Borough1, "Manhattan", "1")


BK <- nyc %>% filter(Borough=="Brooklyn")
BK1 <- BK %>% mutate(Borough=str_replace(Borough, "Brooklyn", "3"))
BK2 <- nyc %>% filter(Borough1=="Brooklyn")
BK2 <- BK2 %>% mutate(Borough1, "Brooklyn", "3")


QN <- nyc %>% filter(Borough=="Queens")
QN1 <- QN %>% mutate(Borough=str_replace(Borough, "Queens", "4"))
QN2 <- nyc %>% filter(Borough1=="Manhattan")
QN2 <- QN2 %>% mutate(Borough1, "Queens", "4")

ST <- nyc %>% filter(Borough=="Staten Island")
ST1 <- ST %>% mutate(Borough=str_replace(Borough, "Staten Island", "5"))
ST2 <- nyc %>% filter(Borough1=="Staten Island")
ST2 <- ST2 %>% mutate(Borough1, "Staten Island", "5")




#nyc1 <- nyc %>% mutate(Borough = str_replace(c(Borough, "Manhattan", "1", "Bronx", "2", "Brooklyn", "3", "Queens", "4"))

#PA2 <- PA1 %>% filter(Applicant.Type!="State Government")


#barrios_vacant_land <- dat %>% group_by(vacantbuil) %>% count() #1888 vacant buildings
#vacant_barrios <- dat %>% group_by(neighborhood) %>% count()

#dat %>% filter(vacantbuil==TRUE) %>% group_by(neighborhood) %>% count() %>% arrange(desc(n))

##Northside has the most vacant lots!!!


#top_barrio <- dat %>% filter(vacantbuil==TRUE) %>% group_by(neighborhood) %>% count() %>% arrange(desc(n)) %>%
  #head(1) %>% pull(neighborhood) 
```




Now, Create the HeatMap

```{r}
#install.packages("tigris")
#install.packages("osmdata")
#install.packages("spData")
#install.packages("spDataLarge")
```


```{r}
#install.packages("ggmap")


library(ggmap)
library(tigris)
library(dplyr)
library(leaflet)
library(sp)
library(ggmap)
library(maptools)
library(broom)
library(httr)
library(rgdal)
library(osmdata)
library(tmap)
library(sf)
library(spData)
#library(spDataLarge)




```

Again
```{r}

nyc <- read_sf("https://data.cityofnewyork.us/api/geospatial/tqmj-j8zm?method=export&format=GeoJSON")


```


```{r}
nyc

```
Need to label the new column with: boro_code
5: Staten Island
2: Bronx
3: Brooklyn
1: Manhattan
4: Queens


```{r}
OLD_MAR <- par()$mar
par(mar = rep(0, 4))
plot(nyc$geometry, border = NA, col = alpha(nyc$boro_code, .2))
legend("topleft",
       legend = nyc$boro_name, col = nyc$boro_code,
       pch = 15,
       bty = "n")
```

```{r}
plot(nyc$geometry)

```



```{r}
OLD_MAR <- par()$mar
par(mfrow = c(1, 1), mar = c(0, 0, 0, 0))
plot(nyc$geometry)
```




IGNORE PLAYING WITH GGPLOT (i STILL DONT GET IT)


Prettier Graph Visualizations

Q2
```{r}
#library(wesanderson)
#paint <- wes_palette("GrandBudapest2", n=3, type="continuous")

slices <- c(16, 13, 2)
Responses <- c("No", "Yes", "Unknown")
pct <- round(slices/sum(slices)*100)
Responses <- paste(Responses, pct) # add percents to labels
Responses <- paste(Responses,"%",sep="")

df <- data.frame(slices, Responses, pct)



ggplot(df, aes(x="", y = "Total of 31 Observations", fill = Responses)) + geom_col(color = "black") +
  geom_label(aes(label = pct),
             color = "black",
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  coord_polar(theta = "y") + scale_fill_manual(values = c("#143151", "#5A435F",
                               "#C3C7E0")) + ggtitle("Number of NYC Neighborhood Specific Clients \n in GSAPP Studios from 2017-2022")
   
   
#to generate random colors use: + scale_fill_brewer()



```


```{r}
#Q3 <- studio %>% count(BIPOC.US.community.)

slices <- c(17, 10, 1, 3)
Responses <- c("No", "Yes", "Unknown", "No and Yes")
pct <- round(slices/sum(slices)*100)
Responses <- paste(Responses, pct) # add percents to labels
Responses <- paste(Responses,"%",sep="")

df1 <- data.frame(slices, Responses, pct)



ggplot(df1, aes(x="", y = "Total of 31 Observations", fill = Responses)) + geom_col(color = "black") +
  geom_label(aes(label = pct),
             color = "white",
             position = position_stack(vjust = 0.5),
             show.legend = FALSE) +
  coord_polar(theta = "y") + scale_fill_manual(values = c("#143151", "#5A435F",
                               "#C3C7E0", "#0A0C18")) + ggtitle("Total Percentage of BIPOC Clients in \n GSAPP Studios from 2017-2022")




```

```{r}
Q4 <- studio %>% count(CBO.Grassroots.Advocacy.Client.from.BIPOC.Community.)
```

```{r}
Q5 <- studio %>% count(Significant.community.engagement...2.3.or.more.site.visits..ideally.3..to.the.same.neighborhoods.AND.multiple.engagements.with.residents..small.merchants..community.leaders..organizations..and.stakeholders.)
```

```{r}
Q6 <- studio %>% count(Ongoing.studio.project.)
```


```{r}

```




```{r}
library(wesanderson)
paint <- wes_palette("GrandBudapest2", n=8, type="continuous")

concerns <- words100 %>% slice_max(freq, n=8) #table with 30 rows and columns
concerns %>% ggplot(aes(x=word, y=freq)) + geom_col() + geom_bar(stat='identity', fill=paint) + ggtitle("The Top 8 Community Concerns Recorded 1 Year After Hurricane Maria")
```

